Discovering Focused Microgenre Communities: Toy example

### 2024-01-06 qmd/04_microgenre-analysis.qmd
Most recent plots and analyses

    age.preds <- pred.probs(x = "age.n", res.salsa$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-salsa.png"), 
              fig = p,
              height = 25, width = 20)
```
`

>>>>

    age.preds <- pred.probs(x = "age.n", res.salsa$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-salsa.png"), 
              fig = p,
              height = 25, width = 20)
```

```{r Microgenre Regression Models (Supp.)}
    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
              "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Age-Squared", 
                            "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.folk <- genre.reg.mods("Folk", k = 4, xvars = spec)
    res.indie <- genre.reg.mods("Indie_Alt", k = 4, xvars = spec)

    tab_model(res.folk$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-folk.html"))
    #webshot(here("Tabs", "reg-tab-folk.html"), here("Tabs", "reg-tab-folk.png"))

    tab_model(res.indie$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-indie.html"))
    #webshot(here("Tabs", "reg-tab-indie.html"), here("Tabs", "reg-tab-indie.png"))

```{r Microgenre Regression Plots (Age/Supp.)}
    age.preds <- pred.probs(x = "age.n", res.folk$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.02,
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-folk.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.indie$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.05,
                    yl = .25, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-indie.png"), 
              fig = p,
              height = 25, width = 20)
```
